---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
```{r load_packages, include = FALSE}
library(raster)
```
# ColorAR

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/agarciaEE/ColorAR.svg?branch=main)](https://travis-ci.com/agarciaEE/ColorAR)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/agarciaEE/ColorAR?branch=main&svg=true)](https://ci.appveyor.com/project/agarciaEE/ColorAR)
[![Codecov test coverage](https://codecov.io/gh/agarciaEE/ColorAR/branch/main/graph/badge.svg)](https://app.codecov.io/gh/agarciaEE/ColorAR?branch=main)
<!-- badges: end -->

The goal of ColorAR is to provide a set of functions to compute coloration metrics from images and perform comparative analyses.

## Installation

You can install the development version of ColorAR like so:

``` r
library(devtools)
install::github("agarciaEE/ColorAR")

```

## Example

This is a basic example which shows you some functions:


```{r load data}
# load package
library(ColorAR)

# get data
data("imgTransList")
```

Compute color proportion of an image:

```{r color_proportion_example}
targetColor <- c(255, 165, 0) #orange RGB code

Orange_proportion <- extractColor(imgTransList[[1]], targetColor)

print(Orange_proportion$P) # print proportion
plot(Orange_proportion$ras) # plot color distribution on the image
```

Classify image based on target colors: 

```{r color_classification_example}
# define a data frame with the target colors RGB codes.
targetColors = data.frame(red = c(255, 255, 0),
                 green = c(255, 165, 0),
                 blue = c(255, 0, 0),
                 row.names = c("white", "orange", "black"))
  
imgClass <- classifyColor(imgTransList[[1]], RGB = targetColors, allow.admixture = F, output = "both")

par(mfrow = c(1,2))
plot(imgClass$class) # plot classified image
plotRGB(imgClass$RGB) # plot classified image in RGB format

```

Perform PCA on images:

```{r color_PCA_example}

## basic example code
imgPCA12 <-  imagePCA(imgTransList, PCx = 1, PCy = 2, scale = F, plot.eigen = F, plot.PCA = F,interpolate = 5, plot.names = F, plot.images = F, plot.tree = NULL, type = "RGB" , as.RGB = F)

```

Plot image PCA along with a tree:

```{r plot_PCA_example}
regcols <- setNames(rep(viridis::inferno(5))[as.factor(dataset$region)], dataset$sample)

imagePCA.plot(imgPCA12, tree = tree, plot.tree = "integrated", plot.images = F, colPCA = regcols, coltree = regcols)
```


